\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2023-02-12 Latex/paper.tex
I forgot a comma
# last version of the paper and refactoring

\usepackage[round]{natbib}
\bibpunct[, ]{(}{)}{;}{a}{}{,}
\let\bibfont\relax
\def\bibfont{\fontsize{8}{10}\selectfont}
\setlength{\bibsep}{0pt}

@@

\affil[1]{CaixaBank, Quantitative Analyst Team, Plaza de Castilla, 3, 28046 Madrid, Spain}
\affil[2]{Facultat de Matem\`{a}tiques i Inform\`{a}tica, Universitat de Barcelona, \authorcr Gran Via 585, 08007 Barcelona, Spain,\vspace*{3pt}}
\affil[3]{VidaCaixa S.A., Market Risk Management Unit, \authorcr C/Juan Gris, 2-8, 08014 Barcelona, Spain.}

@@

The structure of the paper is as follows. In Section \ref{sec:Notation}, we give the basic preliminaries and our notation related to Interest Rates models. This notation will be used throughout the paper without being repeated in particular theorems unless we find it useful to do so in order to guide the reader through the results. In Section \ref{sec:Malliavin}, we make an introduction to Malliavin calculus. In Section \ref{sec:CA}, In Section \ref{sec:Numerical Results}, In Section \ref{sec:Conclusion}

@@

\section{Convexity Adjustment}\label{sec:CA}
In this section, we derive the convexity adjustment for different products. The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula for the convexity adjustment. In order to introduce a general idea of the method. Let define a $Z_t = f(x_t)$. Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$ and that we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure such that $\frac{d\mathbb{Q}_2}{d\mathbb{Q}_1} = \lambda_t$.

Since the convexity adjustment is derived for the Cheyette model, it can be applied to all included models, such as the Hull-White model.

@@

\eqref{forward_rate} and \eqref{future}, we can express the convexity adjustment definition as:%From \eqref{forward_rate} and \eqref{future}, we will define the convexity adjustment as

@@

\subsection{OIS futures}
In this we will derive the covexity adjustment for overnight-indexed swap (OIS) under. We will define for $t_0 < t_1$
\begin{align*}
R(t_0,t_1) &= \frac{\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1}{t_1 - t_0} \\
R_{avg}(t_0,t_1) &= \frac{\int_{t_0}^{t_1}r_{ois,u} du}{t_1 - t_0}.
\end{align*}
We must observe, that both $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictible and they are only observable in $t_1$. However, since
$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$, we can considerer the expected value under the measure $\mathbb{Q}$ that will observable during whole period $[t_0, t_1]$. Let us define the next $\mathbb{Q}$ martingales  
\begin{align*} 
\bar{R}(t,t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left( R(t_0,t_1)  \right) \\
\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
\end{align*}
We must do several obeservations. The first observation is that, if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that
\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1}{t_1 - t_0}, \quad t \in [0,t_0] \\
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{t_1 - t_0} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
\end{align*}
The can define the convexity adjustment for $ R(t_0,t_1)$ the next way
\begin{equation}\label{R_ois_ca}
CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1) 
\end{equation}
The second observation, is that under the dyam we must do is that
\begin{equation}\label{R_ois_avg}
\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  
\end{equation}
In order to compute $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1\right)$, we will define
\begin{equation*}
I(t_0,t_1) = \int_{t_0}^{t_1} r_s ds
\end{equation*}
If we take $D_s$ on $I(t_0,t_1)$ we have that
\begin{equation*}
D_sI(t_0,t_1) = \int_{\max(s, t_{0})}^{t_1}  D_s x_u du 
\end{equation*}
Now, if $t < t_0$, then from (\ref{clark-okone}) and (\ref{approximation_spot_E_s_x_t}), we have that 
\begin{align}\label{apprx_I_t0_t1}
I(t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) \bar{M}(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
&\approx \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,x_0,\bar{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
&= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1} g(s)h(s,x_0,\bar{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
\end{align}
Then, using the previous approximation, we get that
\begin{align*}
1 + \delta_{t_0,t_1}\mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) &= \mathbb{E}_t^{\mathbb{Q}}\left( \exp(I(t_0,t_1)) \right)\\
&\approx \exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)  \mathbb{E}^{\mathbb{Q}}\left(\exp\left(\int_{t}^{t_1} \Gamma(s,t_0,t_1)dW_s^{\mathbb{Q}}\right)\right)
\end{align*}
where $\Gamma(s,t_0,t_1)= g(s)h(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$. 
Since, the Girsanov's theorem (see (\ref{girsanov_spot_forward}))
\begin{equation}\label{representation_i_0_t}
1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{t}^{t_1}\frac{ \Gamma^{2}(s,t_0,t_1)}{2} ds\right)
\end{equation}
Therefore

\hspace{2cm}
\fboxsep1em
\fbox{\parbox{335pt}
{
\begin{equation}\label{convexity_ois_future}
\mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \frac{\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}}
\end{equation}
}}
In order to get an approximation of $\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right)$ with base $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)$, we must note that 
\begin{equation*}
\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left( \log(1+ \delta_{t_0,t_1} R(t_0,t_1))\right)}{ \delta_{t_0,t_1}}.
\end{equation*}
Then from (\ref{representation_i_0_t}) we get that
\begin{equation}\label{convexity_avg_ois_future}
\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} + \frac{\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
\end{equation}
The last step, is to use the basic inequality $\log(1+x) \approx x$
when $x \approx 0$. If we do that, we get the next approximation for $\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right)$

\fboxsep1em
\fbox{\parbox{300pt}
{
\begin{equation*}\label{convexity_avg_ois_future}
\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) \approx  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) + \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}.
\end{equation*}
}}

@@

\begin{example}\label{example_convexity_hw_ois}
The same way that in the example (\ref{example_ca_future}), we will suppose a Hull-White model with constan mean reversion $k=0.003$ and volatility $\sigma=0.01$. It is easy to show in the case of the Hull-White model
\begin{align*}
\Gamma(s,t_0,t_1) &= \frac{\sigma \exp(-ks)}{k}\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1-s))\right)\\
\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)&=-\log\left(\frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) + \frac{\sigma^{2}}{2k^{2}}\left(\delta_{t_0,t_1} - 2 \frac{\exp(-kt_0) - \exp(-kt_1)}{k} + \frac{\exp(-2kt_0) - \exp(-2kt_1)}{k}  \right).
\end{align*}
Therefore we have that
\begin{align*}
\frac{\int_{0}^{t_1} \Gamma^{2}(s,t_0,t_1) ds}{2} &= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_1}  \exp(-2ks)\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1 - s))\right)^{2} ds \\
&= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_0} \exp(-2ks)\left(\exp(-k(t_0 - s)) - \exp(-k(t_1 - s))\right)^{2} ds\\
&+ \frac{\sigma^{2}}{2k^{2}} \int_{t_0}^{t_1} \exp(-2ks)\left(1 - \exp(-k\delta_{t_0,t_1})\right)^{2} ds\\
&= \frac{\sigma^{2}t_0}{2k^{2}} \left( \exp(-kt_0) + \exp(-2kt_1) - 2 \exp(-k(t_1+t_0)) \right)\\  
&+ \frac{\sigma^{2}}{2k^{2}} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k} + \exp(-2kt_1)\delta_{t_0,t_1} - 2\frac{\exp(-k(t_0 + t_1)) - \exp(-kt_1)}{k}  \right)
\end{align*}
Then, if we substitute the last equalities in (\ref{convexity_ois_future}) we get an approximation for OIS future at $t=0$. The next figure, show accuracy of (\ref{convexity_ois_future}) for the particular case of a Hull-White model.

\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.2]{Figures/convexity_ois.jpg}
		\caption{Convexity Mc Vs Convexity Malliavin}
	\end{center}
\end{figure}

@@

@@

% TODO: Change bibliographystyle according to the journal style - it should know the online entry, see Matsuda04
\bibliographystyle{spbasic}
\bibliography{references/references,references/references-books,references/references-own,references/references-online}
%\bibliography{references-export}

>>>>

\usepackage[round]{natbib}
\bibliographystyle{spbasic}
\bibpunct[, ]{(}{)}{;}{a}{}{,}
\let\bibfont\relax
\def\bibfont{\fontsize{8}{10}\selectfont}
\setlength{\bibsep}{0pt}

@@

\affil[1]{CaixaBank, Quantitative Analyst Team, Plaza de Castilla, 3, 28046 Madrid, Spain,}
\affil[2]{Facultat de Matem\`{a}tiques i Inform\`{a}tica, Universitat de Barcelona, \authorcr Gran Via 585, 08007 Barcelona, Spain,\vspace*{3pt}}
\affil[3]{VidaCaixa S.A., Market Risk Management Unit, \authorcr C/Juan Gris, 2-8, 08014 Barcelona, Spain.}

@@

The structure of the paper is as follows. In Section \ref{sec:Notation}, we give the basic preliminaries and our notation related to Interest Rates models. This notation will be used throughout the paper without being repeated in particular theorems unless we find it useful to do so in order to guide the reader through the results. In Section \ref{sec:Malliavin}, we make an introduction to Malliavin calculus. In Section \ref{sec:CA}, we compute the convexity adjsustment for several payoffs that are presents as usual way in the interest rate trading desks. As well, we do some numerical expresents to check the analytical results obtained. To end, in Section \ref{sec:Conclusion} we give the conclusions of the paper and future lines of research to explore.

@@

\section{Convexity Adjustment}\label{sec:CA}
In this section, we derive the convexity adjustment for different products. The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula . In order to introduce a general idea of the method. Let define a $Z_t = f(x_t)$. Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$ and that we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$. Then, if we use the Clark-Ocone representation, we have that
f(x_t) = \mathbb{E}^{\mathbb{Q}_1}\left(f(x_t)\right) + \int_{0}^{t} \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) dW^{\mathbb{Q}_1}_s
Now, if we take $\mathbb{E}^{\mathbb{Q}_2}\left( \cdot \right)$ in the previous expression and we use the Girsanov's theorem, we get that
\begin{equation}\label{general_convexity}
\mathbb{E}^{\mathbb{Q}_2}\left( f(x_t) \right) = f(x_0) + \mathbb{E}^{\mathbb{Q}_1} \left(\int_{0}^{t}  \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) \lambda_s ds \right). 
The second term, is the convexity adjustment to due to change of measure from $\mathbb{Q}_1$ to $\mathbb{Q}_2$. The differents choice of $f$, $\mathbb{Q}_1$ and $\mathbb{Q}_2$ will allow us to get an approximation of the convexity adjustment for the different case of interest. 

@@

\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is:

@@

\subsection{OIS futures}
In this we will derive the covexity adjustment for overnight-indexed swap (OIS) under. We will define for $t_0 < t_1$
\begin{align*}
R(t_0,t_1) &= \frac{\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1}{t_1 - t_0} \\
R_{avg}(t_0,t_1) &= \frac{\int_{t_0}^{t_1}r_{ois,u} du}{t_1 - t_0}.
\end{align*}
We must observe, that both $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictible and they are only observable in $t_1$. However, since
$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$, we can considerer the expected value under the measure $\mathbb{Q}$ that will observable during whole period $[t_0, t_1]$. Let us define the next $\mathbb{Q}$ martingales  
\begin{align*} 
\bar{R}(t,t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left( R(t_0,t_1)  \right) \\
\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
\end{align*}
We must do several obeservations. The first observation is that, if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that
\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1}{t_1 - t_0}, \quad t \in [0,t_0] \\
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{t_1 - t_0} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
\end{align*}
The can define the convexity adjustment for $ R(t_0,t_1)$ the next way
\begin{equation}\label{R_ois_ca}
CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1) 
\end{equation}
The second observation, is that under the dyam we must do is that
\begin{equation}\label{R_ois_avg}
\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  
\end{equation}
In order to compute $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1\right)$, we will define
\begin{equation*}
I(t_0,t_1) = \int_{t_0}^{t_1} r_s ds
\end{equation*}
If we take $D_s$ on $I(t_0,t_1)$ we have that
\begin{equation*}
D_sI(t_0,t_1) = \int_{\max(s, t_{0})}^{t_1}  D_s x_u du 
\end{equation*}
Now, if $t < t_0$, then from (\ref{clark-okone}) and (\ref{approximation_spot_E_s_x_t}), we have that 
\begin{align}\label{apprx_I_t0_t1}
I(t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) \bar{M}(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
&\approx \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,x_0,\bar{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
&= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1} g(s)h(s,x_0,\bar{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
\end{align}
Then, using the previous approximation, we get that
\begin{align*}
1 + \delta_{t_0,t_1}\mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) &= \mathbb{E}_t^{\mathbb{Q}}\left( \exp(I(t_0,t_1)) \right)\\
&\approx \exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)  \mathbb{E}^{\mathbb{Q}}\left(\exp\left(\int_{t}^{t_1} \Gamma(s,t_0,t_1)dW_s^{\mathbb{Q}}\right)\right)
\end{align*}
where $\Gamma(s,t_0,t_1)= g(s)h(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$. 
Therefore, we have that
\begin{equation}\label{representation_i_0_t}
1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(-\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right)
\end{equation}
Therefore

\hspace{2cm}
\fboxsep1em
\fbox{\parbox{335pt}
{
\begin{equation}\label{convexity_ois_future}
\mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \frac{\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(-\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}}
\end{equation}
}}
In order to get an approximation of $\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right)$ with base $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)$, we must note that 
\begin{equation*}
\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left( \log(1+ \delta_{t_0,t_1} R(t_0,t_1))\right)}{ \delta_{t_0,t_1}}.
\end{equation*}
Then from (\ref{representation_i_0_t}) we get that
\begin{equation}\label{convexity_avg_ois_future}
\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} - \frac{\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
\end{equation}
The last step, is to use the basic inequality $\log(1+x) \approx x$
when $x \approx 0$. If we do that, we get the next approximation for $\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right)$

\fboxsep1em
\fbox{\parbox{300pt}
{
\begin{equation}\label{convexity_avg_ois_future}
\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) \approx  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) - \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}.
\end{equation}
}}

@@

\begin{example}\label{example_convexity_hw_ois}
The same way that in the example (\ref{example_ca_future}), we will suppose a Hull-White model with constan mean reversion $k=0.003$ and volatility $\sigma=0.01$. It is easy to show in the case of the Hull-White model
\begin{align*}
\Gamma(s,t_0,t_1) &= \frac{\sigma \exp(-ks)}{k}\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1-s))\right)\\
\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)&=-\log\left(\frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) + \frac{\sigma^{2}}{2k^{2}}\left(\delta_{t_0,t_1} - 2 \frac{\exp(-kt_0) - \exp(-kt_1)}{k} + \frac{\exp(-2kt_0) - \exp(-2kt_1)}{k}  \right).
\end{align*}
Therefore we have that
\begin{align*}
\frac{\int_{0}^{t_1} \Gamma^{2}(s,t_0,t_1) ds}{2} &= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_1}  \exp(-2ks)\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1 - s))\right)^{2} ds \\
&= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_0} \exp(-2ks)\left(\exp(-k(t_0 - s)) - \exp(-k(t_1 - s))\right)^{2} ds\\
&+ \frac{\sigma^{2}}{2k^{2}} \int_{t_0}^{t_1} \exp(-2ks)\left(1 - \exp(-k\delta_{t_0,t_1})\right)^{2} ds\\
&= \frac{\sigma^{2}t_0}{2k^{2}} \left( \exp(-kt_0) + \exp(-2kt_1) - 2 \exp(-k(t_1+t_0)) \right)\\  
&+ \frac{\sigma^{2}}{2k^{2}} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k} + \exp(-2kt_1)\delta_{t_0,t_1} - 2\frac{\exp(-k(t_0 + t_1)) - \exp(-kt_1)}{k}  \right)
\end{align*}(we have to review this integral).
Then, if we substitute the last equalities in (\ref{convexity_ois_future}) we get an approximation for OIS future at $t=0$. The next figure, show accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}) for the particular case of a Hull-White model.
\begin{figure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[scale=0.2]{Figures/convexity_ois.jpg}
		\caption{Convexity Mc Vs Convexity Malliavin}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[scale=0.2]{Figures/convexity_avg_ois.jpg}
		\caption{Convexity Avg Mc Vs Convexity Avg Malliavin}
\end{subfigure}
\caption{Convexity adjustment for compounding and average OIS}
\end{figure} 
\end{example}

@@

\section{Conclusions}\label{sec:Conclusion}

@@

\section{Order of the approximation $\bar{y}_t$}
Under the assumption of $\eta(t,\cdot,\cdot)$ is Lipschitz and with first derive continuous, we have that

\section{Order of the approximation $\bar{x}_t$}

% TODO: Change bibliographystyle according to the journal style - it should know the online entry, see Matsuda04
\bibliography{references/references, references/references-books,references/references-own,references/references-online}
%\bibliography{references-export}
